Meta RL analyses

### 2019-02-01 meta_RL_analyses.Rmd
A few plots for the ARRR

@@

>>>>

```{r}
summary_plot(reward_d %>%
               filter(epoch == 0,
                      run_type == "basic"),
             "game_type", "reward", "is_new_game",
             simple_baselines) 
ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic.png", width=5, height=3)
```

@@

```{r}
ggplot(avg_sweep_d %>%
         filter(run_type == "basic"), aes(x=size, color=is_new_game, y=avg_reward)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi)) +
  scale_color_brewer(palette="Set2") +
  xlab("Meta Set Size") +
  facet_wrap(~ game_type)

ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_sweeping.png", width=5, height=3)
```
